On centrality of orthogonal $\Kt$

### 2016-04-20 paper.tex
Minor

\title{A local-global principle for $K_2$ of $\GL_4$ and orthogonal groups}
\keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}

@@

\date {\today}

@@

\begin{abstract} To be written. \end{abstract}

@@

The main goal of the present paper is to give a uniform proof of centrality of $\mathrm K_2$ for all simply-laced Chevalley groups of rank $\geq3$.\footnote{The authors acknowledge support of ER-EN-EF.}

@@

\section{Case of $\mathrm A_3$}

@@

Suslin showed that (already for $n\geq3$) the elementary group coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
$$
\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},
$$
where $\Um(n,\,R)$ is a set of unimodular coloumns of $R^n$, i.e., such that their entries generate the unit ideal of $R$, $u^t$ stands for $u$ {\it transposed}~\cite{Sus}. This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$. Then, van der Kallen developed Suslin's ideas and showed that the Steinberg group $\St(n,\,R)$ is isomorphic to a group defined by a set of generators
$$
\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}
$$
and relations
\setcounter{equation}{0}
\renewcommand{\theequation}{K\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v')
\end{align}
for $n\geq4$~\cite{vdK}. Then, it is also obvious that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension. Observe that van der Kallen uses pairs of a coloumn and a row $(i,\,j)$ to parametrise his generators, and we prefer two coloumns.

>>>>

\title{On centrality of orthogonal $\Kt$}
\keywords {Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09}

@@

\date {\today}
\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}

@@

\begin{abstract} We give a short uniform proof of centrality of $\mathrm K_2(\Phi, R)$ for all simply-laced root systems $\Phi$ of rank $\geq 3$.
\end{abstract}

@@

@@

\section{Principal notation}

@@

Suslin showed that (already for $n\geq3$) the elementary group coincides with the subgroup of $\GL(n,\,R)$ generated by matrices
$$\{t(u,\,v)=1+uv^t\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\},$$
where $\Um(n,\,R)$ is a set of unimodular coloumns of $R^n$, i.e., such that their entries generate the unit ideal of $R$, $u^t$ stands for $u$ {\it transposed}~\cite{Sus}.
This result clearly implies that $\E(n,\,R)$ is normal inside $\GL(n,\,R)$.
Then, van der Kallen developed Suslin's ideas and showed that the Steinberg group $\St(n,\,R)$ is isomorphic to a group defined by a set of generators
$$\{X(u,\,v)\mid u\in\Um(n,\,R),\ v\in R^n,\ u^tv=0\}$$ and relations
\setcounter{equation}{0} \renewcommand{\theequation}{K\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w),\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v')
\end{align}
for $n\geq4$~\cite{vdK}.
Then, it is also obvious that $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ is a central extension.
Observe that van der Kallen uses pairs of a coloumn and a row $(i,\,j)$ to parametrise his generators, and we prefer two coloumns.
